Breanna_Code

### 2022-09-29 Draft_Report.Rmd
fix  chunkname
histogram chg

```{r histograms with ggplot}
metrics %>% 
  select(!c('Direction', 'Distance')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year'), names_to="Indicator", values_to="value") %>%
  ggplot(aes(x=value)) +
    geom_histogram()+
    facet_wrap(~Indicator, scale="free_x")

@@

metrics %>% 
  select(!c('Direction')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year', 'Distance'), names_to="Indicator", values_to="value") %>%
  ggplot(aes(x=Distance, y=value)) +
    geom_point()+
    facet_wrap(~Indicator, scale="free_y")

@@

```{r scatterplots in ggplot}

@@

## modeling section
```{r models}
# Example model

summary(glmer(`Total Abundance (ind/0.1m²`) ~ DiffuserDirection + DiffuserDistance + DiffuserDirection:DiffuserDistance + (1|Rep), data = Metrics, family = poisson)
```

>>>>

```{r histograms with ggplot}
metrics %>% 
  select(!c('Distance')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year', 'Direction'), names_to="Indicator", values_to="value") %>%
  ggplot(aes(x=value, fill=Direction)) +
    geom_histogram()+
    facet_wrap(~Indicator, scale="free_x")

@@

metrics %>% 
  #select(!c('Direction')) %>%
  pivot_longer(!c( 'Rep', 'Station', 'Year', 'Distance', 'Direction'), names_to="Indicator",  values_to="value") %>%
  ggplot(aes(x=Distance, y=value, fill=Direction)) +
    geom_point()+
    facet_wrap(~Indicator, scale="free_y")

@@

```{r Direction scatterplot}

@@

## modeling section
```{r models}
# Example model
library(lme4)
trialmodel=glmer(`Total Abundance (ind/0.1m²)` ~ DiffuserDirection + DiffuserDistance + DiffuserDirection:DiffuserDistance + (1|Station), data = Metrics, family = poisson)

# no random effects
norfx=glm(`Total Abundance (ind/0.1m²)` ~ DiffuserDirection + DiffuserDistance + DiffuserDirection:DiffuserDistance,  data = Metrics, family = poisson)
```
